### 2017-07-19 introduction.tex
Comments for eamon and some fixed.

Data sensitivity and security concerns are well founded. While many datasets are public, the most
valuable ones are often considered private due to legal or contractual obligations under which the data
is shared, or even governmental restriction. The limited and proprietary nature
of particular datasets can further increase perceived value to researchers given that the space of possible questions and possible answers that can be derived from the data is, in a sense, hidden from competition. At the same time, sensitivity adds the burden of
ensuring the security of the data to the researchers.

% Ability to compute effectively and securely.
To address these concerns, myriad computational infrastructures
have been developed. These infrastructures, including \NAMENS \cite{babuji2016cloud},
implement the software required to securely store and analyze protected
data. However, in almost every case, there is one significant weakness to these systems: the individual humans tasked with administering and managing
data collections are fallible and prone to error. Most often, the policies and processes for managing
the data are ad hoc and lack software support.

To address these challenges we introduce two abstractions:
the `safe-collection' to define the scope of a data collection
and the associated policies and the role of a data `steward'
to manage safe collections. These two constructs allow us
to define, manage, and audit access to, and use of
sensitive data.  We implement these constructs in \NAME and
describe how such implementation enhances security without compromising collaborative agility.

>>>>

Data sensitivity and security concerns are well founded. While many datasets are public, the most
valuable ones are often considered private due to legal or contractual obligations under which the data
is shared, or even governmental regulations. The limited and proprietary nature
of particular datasets can further increase perceived value to researchers given that the space of possible
questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
At the same time, sensitivity adds the burden of ensuring the security of the data to the researchers.

% Ability to compute effectively and securely.
\yadu{a myriad of?}

To address these concerns, myriad computational infrastructures
have been developed. These infrastructures, including \NAMENS \cite{babuji2016cloud},
implement the software required to securely store and analyze protected
data. However, in almost every case, there is one significant weakness to these systems: the individual humans tasked with administering and managing
data collections are fallible and prone to error. Most often, the policies and processes for managing
the data are ad hoc and lack software support.

To address these challenges we introduce two abstractions:
the `safe-collection' to define the scope of a data collection
and the associated policies and the role of a data `steward'
to manage safe collections. These two constructs allow us
to define, manage, and audit access, use, and export of
sensitive data.  We implement these constructs in \NAME and
describe how such implementation enhances security without compromising collaborative agility.
